\documentclass[a4paper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.35in}
\setlength{\footskip}{5pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-3pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\begin{document}

\begin{center}
    {\LARGE \scshape Kifah Andary} \\ \vspace{4pt}
    \small Full Stack Developer \textbar\ Enterprise SaaS, Web3, Secure Backend Systems \\ \vspace{3pt}
    \small \raisebox{-0.1\height}\faPhone\ +961-71-173034 ~ \href{mailto:kifah.andary@gmail.com}{\raisebox{-0.1\height}\faEnvelope\ \underline{kifah.andary@gmail.com}} ~
    \href{https://www.linkedin.com/in/kifahandary/}{\raisebox{-0.1\height}\faLinkedin\ \underline{linkedin.com/in/kifahandary}} ~
    \href{https://github.com/kifah1989}{\raisebox{-0.1\height}\faGithub\ \underline{github.com/kifah1989}}
\end{center}

\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Full Stack Developer with 5+ years of experience building enterprise SaaS platforms, secure web applications, and Ethereum-based products across Java Spring Boot, Angular, React, Node.js, PostgreSQL, and Solidity.}
  \resumeItem{Known for improving performance, hardening security, and shipping production systems, including ERP solutions for UAE B2B clients and live blockchain applications with zero reported security incidents.}
\resumeSubHeadingListEnd

\section{Core Skills}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Core Stack:} Java, Spring Boot, Angular, React, Node.js, PostgreSQL, REST APIs, TypeScript, JavaScript}
  \resumeItem{\textbf{Backend \& Data:} Spring MVC, Express.js, JPA/Hibernate, Liquibase, MySQL, MongoDB, SQL, GraphQL}
  \resumeItem{\textbf{Web3:} Solidity, Ethereum, Smart Contracts, DApp Development, Web3.js, Ethers.js, MetaMask Integration}
  \resumeItem{\textbf{Tools:} AWS, Azure Functions, Docker, Git, Maven, CI/CD, Agile/Scrum}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Full Stack Developer - Remote}{Dec 2024 -- Mar 2026}
    {ERP Data Systems | UAE}{}
    \resumeItemListStart
      \resumeItem{Delivered and enhanced a multi-module ERP platform covering Accounting, Inventory, Project, Procurement, and HR workflows for UAE B2B clients.}
      \resumeItem{Built full-stack features in Spring Boot and Angular, designed database models with JPA/Hibernate and Liquibase, and helped ship production-ready releases in a 5-person team.}
      \resumeItem{Resolved legacy N+1 query bottlenecks, redesigned search and pagination around optimized backend queries, and improved day-to-day application responsiveness.}
      \resumeItem{Strengthened security by removing hardcoded secrets, moving credentials to AWS Secrets Manager, hashing stored passwords, and building an AI chatbot for natural-language SQL data access.}
    \resumeItemListEnd

  \resumeSubheading
    {Web3 Full Stack Developer}{Dec 2021 -- Nov 2024}
    {Aether | Lebanon}{}
    \resumeItemListStart
      \resumeItem{Designed and maintained Ethereum-based DApps using the MERN stack, delivering production-ready user experiences tied to live blockchain transactions.}
      \resumeItem{Authored, tested, and deployed Solidity smart contracts implementing business-critical token and transaction logic with strong reliability and security practices.}
      \resumeItem{Launched and maintained production DApps, including smart contracts for the HILO token listed on CoinMarketCap, with zero reported security incidents.}
    \resumeItemListEnd

  \resumeSubheading
    {Independent Developer \& Contract Roles}{2017 -- 2021}
    {Lebanon / Remote}{}
    \resumeItemListStart
      \resumeItem{Built personal full-stack projects and delivered contract Angular work integrated with Azure Functions, REST APIs, MongoDB, and social authentication flows.}
      \resumeItem{Deepened practical expertise in React, Angular, Node.js, Solidity, and Ethereum, creating the foundation for transition into professional full-stack and Web3 roles.}
    \resumeItemListEnd

  \resumeSubheading
    {Information Technology Officer}{2015 -- 2017}
    {24pluse.ae | UAE}{}
    \resumeItemListStart
      \resumeItem{Provided IT operations support and managed financial data systems, building early enterprise software and systems reliability experience.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education \& Certification}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Arab Open University} -- B.Sc. in Information Technology \& Computing (Software Engineering), 2010 -- 2014}
  \resumeItem{Graduate coursework in Information Security \& Forensics, 2015 -- 2016}
  \resumeItem{\textbf{Certification:} Cisco CCNA, 2014}
\resumeSubHeadingListEnd

\end{document}