\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kifah Andary} \\ \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ +961-71-173034 ~ \href{mailto:kifah.andary@gmail.com}{\raisebox{-0.1\height}\faEnvelope\  \underline{kifah.andary@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/kifahandary/}{\raisebox{-0.1\height}\faLinkedin\ \underline{linkedin.com/in/kifahandary}} ~
    \href{https://github.com/kifah1989}{\raisebox{-0.1\height}\faGithub\ \underline{github.com/kifah1989}} ~ 
\end{center}


%-----------PROFILE SUMMARY-----------
\section{Profile Summary}
\resumeSubHeadingListStart
    \resumeItem{Full Stack Developer with 5+ years of professional experience in Web3 DApp development, smart contract programming, and enterprise ERP solutions.}
    \resumeItem{Delivered production DApps handling live token transactions on Ethereum with zero security incidents; built AI-powered ERP features for the UAE market.}
    \resumeItem{Proficient in Java Spring Boot, Angular, React, Node.js, Solidity, and PostgreSQL with a focus on scalable, secure architecture.}
\resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
\resumeSubHeadingListStart
    \resumeItem{
        \textbf{Programming Languages:}{ Java, TypeScript, JavaScript, Solidity, Python, C, HTML5, CSS3, SQL}
    }
    \resumeItem{
        \textbf{Frontend Technologies:}{ Angular, React, Next.js, Bootstrap, Tailwind CSS, Material-UI}
    }
    \resumeItem{
        \textbf{Backend Technologies:}{ Node.js, Express.js, Spring Boot, Spring MVC, RESTful APIs, GraphQL}
    }
    \resumeItem{
        \textbf{Databases \& Storage:}{ MongoDB, PostgreSQL, MySQL, JPA/Hibernate, Entity Modeling}
    }
    \resumeItem{
        \textbf{Web3 \& Blockchain:}{ Ethereum, Solidity, Smart Contracts, DApp Development, Web3.js, Ethers.js, MetaMask Integration}
    }
    \resumeItem{
        \textbf{DevOps \& Tools:}{ Git, Maven, Docker, AWS, Azure Functions, CI/CD, Postman, VS Code}
    }
    \resumeItem{
        \textbf{Architecture \& Methodologies:}{ MVC, MVVM, Microservices, RESTful Design, Agile/Scrum}
    }
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Full Stack Developer - Remote}{Dec 2024 -- Mar 2026}
    {ERP Data Systems | UAE}{}
    \resumeItemListStart
        \resumeItem{Developed and maintained an enterprise ERP platform spanning 5 core modules (Accounting, Inventory, Project, Procurement, HR), each with comprehensive reporting and filtering tools, serving multiple B2B clients in the UAE.}
        \resumeItem{Built full-stack features using Java Spring Boot and Angular TypeScript within a team of 5, designing complex database schemas with JPA/Hibernate and Liquibase.}
        \resumeItem{Resolved critical N+1 query issues inherited from legacy code, and refactored frontend search and pagination to use optimized backend queries with debounce, significantly improving application responsiveness.}
        \resumeItem{Hardened application security by eliminating hardcoded credentials from the frontend and backend, migrating secrets to AWS Secrets Manager, and hashing plaintext passwords stored in the database.}
        \resumeItem{Created RESTful APIs and a microservices architecture to ensure seamless integration between ERP modules and external systems.}
        \resumeItem{Developed an AI-powered chatbot feature using Spring Boot AI tool calling with an LLM, enabling users to query SQL data in natural language.}
    \resumeItemListEnd
    
  \resumeSubheading
    {Web3 Full Stack Developer}{Dec 2021 -- Nov 2024}
    {Aether | Lebanon}{}
    \resumeItemListStart
        \resumeItem{Designed, developed, and maintained decentralized applications (DApps) on the Ethereum blockchain using the MERN stack.}
        \resumeItem{Authored, tested, and deployed secure and efficient Solidity smart contracts, implementing complex business logic to automate DApp operations.}
        \resumeItem{Collaborated with UX/UI designers to create intuitive and responsive user interfaces, ensuring cross-browser compatibility.}
        \resumeItem{Worked closely with project managers, developers, and stakeholders to deliver projects on time.}
        \resumeItem{\textbf{Key Achievement:} Launched and maintained production DApps handling live cryptocurrency transactions, including smart contracts for the HILO token (listed on CoinMarketCap), with zero security incidents.}
    \resumeItemListEnd

  \resumeSubheading
    {Independent Developer \& Self-Directed Learning}{2017 -- 2021}
    {Self-Employed | Lebanon}{}
    \resumeItemListStart
        \resumeItem{Pursued continuous self-directed learning in full-stack web development, building personal projects published on GitHub.}
        \resumeItem{Studied modern JavaScript frameworks (React, Angular, Node.js) and blockchain development (Solidity, Ethereum).}
        \resumeItem{Developed foundational skills in the MERN stack that directly enabled the transition to professional Web3 development.}
    \resumeItemListEnd

  \resumeSubheading
    {Full Stack Developer -- Contract}{Jun 2017 -- Jul 2017}
    {Remote Contract | Canada}{}
    \resumeItemListStart
        \resumeItem{Developed Angular web applications integrated with Azure Functions and REST APIs for MongoDB and social media authentication.}
        \resumeItem{Collaborated with back-end developers, QA testers, and the CTO on time-sensitive feature deliveries and database upgrades.}
    \resumeItemListEnd
    
  \resumeSubheading
    {Information Technology Officer}{2015 -- 2017}
    {24pluse.ae | UAE}{}
    \resumeItemListStart
        \resumeItem{Provided comprehensive IT support and managed financial data systems, gaining foundational experience in enterprise software.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Arab Open University}{Lebanon}
    {Graduate Coursework in Information Security \& Forensics}{2015 -- 2016}
    \resumeItemListStart
        \resumeItem{Completed 1.5 years of graduate-level studies: Digital Forensics, Network Security, Data Management, Kali Linux, Python, Computer Networking.}
    \resumeItemListEnd
  \resumeSubheading
    {Arab Open University}{Lebanon}
    {B.Sc. in Information Technology \& Computing (Software Engineering)}{2010 -- 2014}
    \resumeItemListStart
        \resumeItem{Coursework: Computer Programming in C, Data Computing \& Information, Information \& Communication Technology.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Key Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Enterprise ERP System} $|$ \emph{Java Spring Boot, Angular, PostgreSQL, AWS}}{2024 -- Present}
        \resumeItemListStart
            \resumeItem{Built a multi-module ERP platform (Accounting, Inventory, Project, Procurement, HR) with advanced reporting and filtering for B2B clients.}
            \resumeItem{Optimized legacy N+1 queries, hardened security (AWS Secrets Manager, password hashing), and developed an AI chatbot for natural language data access.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{DeFi Token Platform} $|$ \emph{React, Node.js, Solidity, Ethereum}}{2022 -- 2023}
        \resumeItemListStart
            \resumeItem{Built a decentralized platform with smart contract integration for the HILO token (listed on CoinMarketCap).}
            \resumeItem{Engineered secure on-chain transaction flows with zero security incidents across the contract lifecycle.}
        \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Cisco CCNA} -- Arab Open University, 2014}
\resumeSubHeadingListEnd


\end{document}